HEP Software Foundation Community White Paper Working Group -- Data Processing Frameworks

### 2018-12-19 CWP/papers/HSF-CWP-2017-08_framework/latex/df_fwk_summary.tex
Final tweaks for arXiv publication (#125)
- Readded the subcaption package as the document would not process without it
- Updated date to date of submisison

\usepackage{graphicx}
% \usepackage{subcaption}
\usepackage{xspace}

@@

\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-CWP-2017-08 \\
 & & December 21, 2017 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{2.0cm}

>>>>

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{xspace}

@@

\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-CWP-2017-08 \\
 & & December 19, 2018 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{2.0cm}
